---
title: "Diagnostic - one model"
author: "Erica Goto"
date: "2/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Library & Dataset
```{r, warning=FALSE,  include=FALSE}
library(MASS)
library(tidyverse)
library(dplyr)
library(readxl)
library(car)
library(stats)
library(nnet)
library(glmnet)
library(boot)
library(nlstools)
library (ggplot2)
library(sf)
library(rstanarm)
library(caret)
library(nnet)
library(sure)
library(Hmisc)
library(stargazer)
library(rms)
library(plyr)

OLR <- read_excel("all.xlsx")

```



Using OLR
```{r, warning=FALSE,  include=FALSE}
OLR <- OLR  %>%  filter(density != "d4") 

OLR$angle <- as.factor(OLR$angle) #it is not factor, categories are independent in order of importance. The same with density
OLR$building <-factor(OLR$building, levels=c("B", "W", "M"), ordered=TRUE) 

#if (OLR$building  == "B") {0}
#if(OLR$building  == "W") {1}
#if(OLR$building  == "M") {2}
#OLR$building <-as.integer(OLR$building)
OLR$EN <- as.logical(OLR$EN)
OLR$density <- as.factor(OLR$density)
OLR$TC <- as.logical(OLR$TC)
OLR$TC_mature_Soil <- as.logical(OLR$TC_mature_Soil)
OLR$TC_saprolito <- as.logical(OLR$TC_saprolito)
OLR$TC_weath_rock <- as.logical(OLR$TC_weath_rock)
OLR$TC_rock <- as.logical(OLR$TC_rock)
OLR$TC_geol_desfav <- as.logical(OLR$TC_geol_desfav)
OLR$Taterro <- as.logical(OLR$Taterro)
OLR$DepEncosta <- as.logical(OLR$DepEncosta)
OLR$DepEncNatural <- as.logical(OLR$DepEncNatural)
OLR$DepTaludeCorte <- as.logical(OLR$DepTaludeCorte)
OLR$DepTaludeAterro <- as.logical(OLR$DepTaludeAterro)
OLR$landfill <- as.logical(OLR$landfill)
OLR$garbage <- as.logical(OLR$garbage)
OLR$construction_deposit <- as.logical(OLR$construction_deposit)
OLR$crack <- as.logical(OLR$crack)
OLR$leaning_wall <- as.logical(OLR$leaning_wall)
OLR$scars <- as.logical(OLR$scars)
OLR$conc_rainfall_water <- as.logical(OLR$conc_rainfall_water)
OLR$downward_floor <- as.logical(OLR$downward_floor)
OLR$tilted <- as.logical(OLR$tilted)
OLR$fracture <- as.logical(OLR$fracture)
OLR$wastewater <- as.logical(OLR$wastewater)
OLR$leak <- as.logical(OLR$leak)
OLR$septic_tank <- as.logical(OLR$septic_tank)
OLR$drainage <- factor(OLR$drainage, levels=c("Y", "P", "N"), ordered=TRUE)
#if(OLR$drainage  == "Y"){0}
#if(OLR$drainage  == "P"){1}
#if(OLR$drainage  == "N"){2}
#OLR$drainage <- as.integer(OLR$drainage)

OLR$tree <- as.logical(OLR$tree)
OLR$ground_veg <- as.logical(OLR$ground_veg)
OLR$deforestation <- as.logical(OLR$deforestation)
OLR$banana <- as.logical(OLR$banana)
OLR$risk <- factor(OLR$risk, levels=c("R1", "R2", "R3", "R4"), ordered=TRUE)


```



##Inspect Dataset Using Training and Validation

```{r, warning=FALSE,  include=FALSE}
#set.seed(1234)
training.samples <- OLR$risk %>%
        createDataPartition(p=0.7, list=FALSE)
train.data  <- OLR[training.samples, ]
test.data <- OLR[-training.samples, ]
```



##OLR Equations
- Using all variables

##Inspect Dataset Using Training and Validation

- Training set divide in the Diagnostic_based.on.Harell.Rmd file

```{r, fig.height=5, fig.width=7}
#vclust <- varclus (~ angle + building+EN +TC + TC_mature_Soil + TC_saprolito +  TC_weath_rock + TC_rock + TC_geol_desfav + Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte + DepTaludeAterro + landfill + garbage + construction_deposit + crack + leaning_wall + scars + downward_floor + tilted + fracture + conc_rainfall_water + wastewater + leak + septic_tank + drainage + tree + ground_veg + deforestation + banana , data=train.data)

# took out density since training has 0 d4 and it was not allowing do the plot

#p <- plot(vclust)
```


```{r, fig.height= 15, fig.width= 5, warning=FALSE}
par(mfrow=c(8,4))
plot.xmean.ordinaly (risk~  angle+ density+building+EN +TC + TC_mature_Soil + TC_saprolito +  TC_weath_rock + TC_rock + TC_geol_desfav + Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte + DepTaludeAterro + landfill + garbage + construction_deposit + crack + leaning_wall + scars + downward_floor + tilted + fracture + conc_rainfall_water + wastewater + leak + septic_tank  + tree + ground_veg + deforestation + banana + drainage, data=train.data, cr=TRUE , subn=FALSE , cex.points =0.65)


#angle + building+density+EN +TC + TC_mature_Soil + TC_saprolito +  TC_weath_rock + TC_rock + TC_geol_desfav + Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte + DepTaludeAterro + aterro + lixo + entulho + crack + belly_wall + scars + drawback + tilted + fracture + conc_rainfall_water + wastewater + leak + septic_tank + drainage + tree + ground_veg + deforestation + banana 
```

Diagnostic 2: Proportion (-5% of one of the parameters based on what is expected. Since some parameters have 2 predictors, others 5)

```{r}

#library(plyr)
angle <- count(train.data$angle) # angle A less than 5% but the rest are okay (3,50, 91, 277, 109) Expected=106
angle <- angle %>%
  mutate("Percentage"=(freq/106)*100)%>%
  mutate("Classifier" = "angle")



building <- count(train.data$building) %>% #(445, 46, 39) 
  mutate ("Percentage"=(freq/176.7)*100)%>%
  mutate("Classifier" = "building")

density <- count(train.data$density)  %>% #(79, 415, 36) # d4 =0 
  mutate ("Percentage"=(freq/132.5)*100)%>%
  mutate("Classifier" = "density")


EN <- count(train.data$EN) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "EN")

TC <- count(train.data$TC)  %>%
  mutate ("Percentage"=(freq/265)*100) %>%
  mutate("Classifier" = "TC")

TC_MatureSoil <- count(train.data$TC_mature_Soil) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "TC_MatureSoil")


TC_Saprolito <- count(train.data$TC_saprolito)  %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "TC_Saprolito")

TC_WRock <- count(train.data$TC_weath_rock) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "TC_WRock")

TC_rock <- count(train.data$TC_rock) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "TC_rock")

TC_geol_desfav <- count(train.data$TC_geol_desfav) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "TC_geol_desfav")

Taterro <- count(train.data$Taterro) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "Taterro")

DepEncNatural <- count(train.data$DepEncNatural) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "TC")

DepTaludeAterro <- count(train.data$DepTaludeAterro) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "DepEncNatural")

DepTaludeCorte <- count(train.data$DepTaludeCorte) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "DepTaludeCorte")

DepTaludeAterro <- count(train.data$DepTaludeAterro) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "DepTaludeAterro")

construction_deposit <- count(train.data$construction_deposit) %>%
  mutate ("Percentage"=(freq/265)*100) %>%
  mutate("Classifier" = "construction_deposit")

garbage <- count(train.data$garbage) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "garbage")

crack <- count(train.data$crack) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "crack")

leaning_wall <- count(train.data$leaning_wall) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "leaning_wall")

scars <- count(train.data$scars) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "DepTaludeAterro")

downward_floor <- count(train.data$downward_floor) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "scars")

tilted <- count(train.data$tilted) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "tilted")

fracture <- count(train.data$fracture) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "fracture")

conc_rainfall_water <- count(train.data$conc_rainfall_water) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "DepTaludeAterro")

leak <- count(train.data$leak) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "conc_rainfall_water")

wastewater <- count(train.data$wastewater) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "wastewater")

septic_tank <- count(train.data$septic_tank) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "septic_tank")

drainage <- count(train.data$drainage) %>%
  mutate ("Percentage"=(freq/176.7)*100)%>%
  mutate("Classifier" = "drainage")

tree <- count(train.data$tree) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "tree")

ground_veg <- count(train.data$ground_veg) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "ground_veg")

deforestation <- count(train.data$deforestation) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "deforestation")

banana <- count(train.data$banana) %>%
  mutate ("Percentage"=(freq/265)*100)%>%
  mutate("Classifier" = "banana")


df <- rbind(TC, TC_MatureSoil, TC_Saprolito, TC_WRock, TC_rock, TC_geol_desfav, Taterro, DepEncNatural, DepTaludeAterro, DepTaludeCorte,construction_deposit, garbage, crack, leaning_wall, 
            scars, downward_floor, tilted, fracture, conc_rainfall_water, leak, wastewater, septic_tank, drainage, tree, ground_veg, deforestation, banana, 
            angle,
            building, density, EN
)

df
```




TC_weath_rock, TC_rock_TC_geol_desf, fracture, TC_rock

- OF: angle (slope angle), building (building material), EN (natural slope), TC_saprolito (cut slope with saprolite), Taterro (slope with landfill), DepEncostaNatural (natural slope with construction material), DepTaludeAterro (slope with landfill and construction material), DepTaludeCorte (cut slope with construction material), landfill, garbage, construction_deposit (construction material), crack, leaning_wall, scars, downward_floor, tilted, conc_rainfall_water (concentration of rainfall water), wastewater, leak, drainage 
- MOF:TC_mature_soil (slope cut with soil), density, TC (slope cut), - - TC_geol_desfav (cut slope with geology favorable to instability), tree, ground_veg (ground vegetation), deforestation, banana 
- NOF: TC_weath_rock (cut slope with weathering rock), TC_rock (cut slope in bedrock), fracture, septic_tank
- GP:all classifiers minus BP classifiers
- BP: TC_weath_rock (True N= 11 , False N=  529), TC_geol_desf (True N= 11 , False N=  529), fracture (True N=1 , False N=529), TC_rock (True N=1 , False N=529 ),  septic_tank (True N=4 , False N=526 )

## Equation 1
- consider all parameter okay from first diagnostic: 

f1 <- lrm(risk ~ building + EN + TC_saprolito +
                  Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte +
                  landfill + garbage + construction_deposit + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + leak + tree + ground_veg + banana
          , data=train.data, x=TRUE , y=TRUE)
          

f1 <- lrm(risk ~ building + EN + TC_saprolito +
                  Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte +
                  landfill + garbage + construction_deposit + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + leak + tree + ground_veg + banana + septic_tank
                  +TC_mature_Soil
          , data=train.data, x=TRUE , y=TRUE)
print (f1 , latex =TRUE , coefs =5)
stargazer(anova(f1), type="text", style="default")

```{r}

# Equation 1

eq_OLR_01 <- polr(risk~ building + TC_saprolito +
                  Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte +
                  landfill + garbage + construction_deposit + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + leak + tree + ground_veg + banana + septic_tank + TC_mature_Soil + deforestation, data= train.data
           ,  method = "logistic", Hess = TRUE)
ctable <- coef(summary(eq_OLR_01))



p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value
ctable <- cbind(ctable, "p value" = p )

ctable
stargazer((ctable), type="text", style="default", digits = 2)

```

less p-value = 0.10 (TC_saprolitoTRUE,TaterroTRUE, DepTaludeAterroTRUE,DepTaludeAterroTRUE,landfillTRUE,  construction_depositTRUE,  leakTRUE)


```{r, fig.height= 9, fig.width= 5}

par(mfrow=c(6,4))
plot.xmean.ordinaly (risk~ building + TC_saprolito +
                  Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte +
                  landfill + garbage + construction_deposit + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + leak + tree + ground_veg + banana + septic_tank + TC_mature_Soil + deforestation
          ,data=train.data, cr=TRUE , subn=FALSE ,  cex.lab=1.5, cex.axis=2, cex.sub=2, cex.main=2)
```






# Creating function with four level 

Equation 1
```{r,  fig.width=5, fig.height=15}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~building + TC_saprolito +
                  Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte +
                  landfill + garbage + construction_deposit + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + leak + tree + ground_veg + banana + septic_tank + TC_mature_Soil + deforestation
, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=1.5, cex.axis=1.5, cex.sub=1.5)

```


## Equation 2
- parameters okay and so/so
- porportion
- excluded TC_geol_desf

f2 <- lrm(risk ~ angle + building + EN + TC_saprolito +
                  Taterro + DepEncNatural + DepTaludeAterro + DepTaludeCorte +
                  landfill + garbage + construction_deposit + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + leak + drainage +
                  TC_mature_Soil + density + TC + 
                  tree +ground_veg + deforestation + banana
          , data=train.data, x=TRUE , y=TRUE)
          
          stargazer(anova(f2), type="text", style="default")


```{r}


eq_OLR_02 <- polr(risk ~ angle +building + EN + TC_saprolito+ Taterro+ TC_mature_Soil+ DepEncNatural+ DepTaludeAterro+  DepTaludeCorte+ landfill+garbage+ construction_deposit+ leak+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ tree+ ground_veg+ banana+ deforestation + density+ TC,
                  
                 data= train.data
           ,  method = "logistic", Hess = TRUE)
ctable <- coef(summary(eq_OLR_02))








p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value
ctable <- cbind(ctable, "p value" = p )

ctable
stargazer((ctable), type="text", style="default", digits=2)
```

```{r, fig.height= 10, fig.width= 5}
par(mfrow=c(7,4))
plot.xmean.ordinaly (risk~ angle +building + EN + TC_saprolito+ Taterro+ TC_mature_Soil+ DepEncNatural+ DepTaludeAterro+  DepTaludeCorte+ landfill+garbage+ construction_deposit+ leak+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ tree+ ground_veg+ banana+ deforestation + density+ TC
          ,data=train.data, cr=TRUE , subn=FALSE ,  cex.lab=1.5, cex.axis=4, cex.sub=4, cex.main=4)


```



```{r,  fig.width=5, fig.height=12}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~angle +building + EN + TC_saprolito+ Taterro+ TC_mature_Soil+ DepEncNatural+ DepTaludeAterro+  DepTaludeCorte+ landfill+garbage+ construction_deposit+ leak+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ tree+ ground_veg+ banana+ deforestation + density+ TC,data=train.data
, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=1, cex.axis=2, cex.sub=1)

```


## Equation 3
- parameters okay and so/so
- porportion
- p-value based equation 2  > 0.5

f3 <- lrm(risk ~ angle +building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ tree + TC
          , data=train.data, x=TRUE , y=TRUE)
stargazer(anova(f3), type="text", style="default")

```{r}

# x=TRUE, y=TRUE used by resid() below 

eq_OLR_03 <- polr(risk ~ building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ground_veg + conc_rainfall_water+tree+ wastewater + TC,
 data= train.data
           ,  method = "logistic", Hess = TRUE)
ctable <- coef(summary(eq_OLR_03))


p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value
ctable <- cbind(ctable, "p value" = p )

ctable


stargazer((ctable), type="text", style="default", digits = 2)
#print (f3 , latex =TRUE , coefs =5)


```



```{r, fig.height=7, fig.width=8}
par(mfrow=c(3,5))
plot.xmean.ordinaly (risk ~  building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ground_veg + conc_rainfall_water+tree+ wastewater + TC,
          data=train.data, cr=TRUE , subn=FALSE , cex.points =0.65)
```


```{r,  fig.width=5, fig.height=9}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ground_veg + conc_rainfall_water+tree+ wastewater + TC, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=0.6, cex.axis=0.6, cex.sub=0.6)

```


## Equation 4
- p-value equation 3 > 0.05 (banana, DepTaludeCorte)
- consider proportion 
- paremeters okay & so/so
- fashion order

f4 <- lrm(risk ~ building + EN  
                   + DepEncNatural   
                    + crack +
                  leaning_wall + scars + downward_floor +tilted +
                  conc_rainfall_water + wastewater + drainage +
                          TC_mature_Soil  + TC + 
                   +ground_veg   
           ,data=train.data, x=TRUE , y=TRUE)
# x=TRUE, y=TRUE used by resid() below 
#print (f4 , latex =TRUE , coefs =5)
stargazer(anova(f4), type="text", style="default")

```{r}




eq_OLR_04 <- polr(risk~  building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ground_veg + conc_rainfall_water+ wastewater + TC
                  , data= train.data
           ,  method = "logistic", Hess = TRUE)
p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value

ctable <- coef(summary(eq_OLR_04))

ctable <- cbind(ctable, "p value" = p )

ctable
stargazer((ctable), type="text", style="default", digits=2)

```



```{r, fig.height=7, fig.width=7}
par(mfrow=c(4,4))
plot.xmean.ordinaly (risk ~  building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ground_veg + conc_rainfall_water+ wastewater + TC
          ,data=train.data, cr=TRUE , subn=FALSE , cex.points =0.65)
```



```{r,  fig.width=8, fig.height=8}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~building + EN + DepTaludeAterro+  DepTaludeCorte+ crack+ leaning_wall+ scars+ downward_floor+ tilted+ground_veg + conc_rainfall_water+ wastewater + TC
, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=0.7, cex.axis=0.5, cex.sub=0.5)

```






## Equation 5 - Based on Equation 1

- based on Eq 1 
- less p-value > 0.10 (

```{r}

# x=TRUE, y=TRUE used by resid() below 
#print (f1 , latex =TRUE , coefs =5)
#stargazer(anova(f1), type="text", style="default")

eq_OLR_05 <- polr(risk ~ building+ TC_mature_Soil+ DepTaludeAterro+  DepTaludeCorte+  construction_deposit+  crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ ground_veg,  data= train.data
           ,  method = "logistic", Hess = TRUE)

ctable <- coef(summary(eq_OLR_05))

p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value
ctable <- cbind(ctable, "p value" = p )

ctable
stargazer((ctable), type="text", style="default", digits = 2)

```




```{r, fig.height=7, fig.width=8}
par(mfrow=c(3,5))
plot.xmean.ordinaly (risk ~  building+ TC_mature_Soil+ DepTaludeAterro+  DepTaludeCorte+  construction_deposit+  crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ ground_veg
          ,data=train.data, cr=TRUE , subn=FALSE , cex.points =0.65)
```



```{r,  fig.width=8, fig.height=8}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~building+ TC_mature_Soil+ DepTaludeAterro+  DepTaludeCorte+  construction_deposit+  crack+ leaning_wall+ scars+ downward_floor+ tilted+ conc_rainfall_water+ wastewater+ ground_veg
, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=0.7, cex.axis=0.5, cex.sub=0.5)

```



##OLR Equation 6
- based on Equation 5 (less  +construction_deposit,  DepTaludeAterro )
- p >0.5



```{r}

# x=TRUE, y=TRUE used by resid() below 
#print (f1 , latex =TRUE , coefs =5)
#stargazer(anova(f1), type="text", style="default")

eq_OLR_06 <- polr(risk ~ building+ TC_mature_Soil+  DepTaludeCorte+  conc_rainfall_water +  crack+ leaning_wall+ scars+ downward_floor+ tilted + wastewater+ ground_veg,  data= train.data
           ,  method = "logistic", Hess = TRUE)

ctable <- coef(summary(eq_OLR_06))

p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value
ctable <- cbind(ctable, "p value" = p )

ctable
stargazer((ctable), type="text", style="default", digits = 2)

```



```{r, fig.height=5, fig.width=7}
par(mfrow=c(3,4))
plot.xmean.ordinaly (risk ~  building+ TC_mature_Soil+  DepTaludeCorte+  conc_rainfall_water +  crack+ leaning_wall+ scars+ downward_floor+ tilted + wastewater+ ground_veg
          ,data=train.data, cr=TRUE , subn=FALSE , cex.points =0.65)
```


```{r,  fig.width=7, fig.height=7}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~building+ TC_mature_Soil+  DepTaludeCorte+  conc_rainfall_water +  crack+ leaning_wall+ scars+ downward_floor+ tilted + wastewater+ ground_veg
, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=0.7, cex.axis=0.5, cex.sub=0.5)

```


Equation 07


- parameters okay and so/so
- porportion
- collinearity 



f7 <- lrm(risk~options(contrasts=c(1,2,3), building)+ angle+EN+TC+ TC_mature_Soil+banana+TC_saprolito+ garbage+ landfill + construction_deposit + drainage + leak+ conc_rainfall_water+ crack+ tilted + leaning_wall + scars + tree + ground_veg
                  , data= train.data, x=TRUE , y=TRUE)
# x=TRUE, y=TRUE used by resid() below 
#print (f4 , latex =TRUE , coefs =5)
stargazer(anova(f6), type="text", style="default")


```{r}



eq_OLR_07 <- polr(risk~ angle+ building+ EN+ TC+ landfill+ garbage+ construction_deposit+ crack+ leaning_wall + scars+ tilted+ conc_rainfall_water+ leak+ tree+ wastewater+  ground_veg+  banana
                  , data= train.data
           ,  method = "logistic", Hess = TRUE)
p<- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE*2) #computes p value

ctable <- coef(summary(eq_OLR_07))

ctable <- cbind(ctable, "p value" = p )

ctable
stargazer((ctable), type="text", style="default", digits = 2)

```


```{r, fig.height=8, fig.width=7}
par(mfrow=c(5,4))
plot.xmean.ordinaly (risk ~   building+ angle+ EN+ TC+ landfill+ garbage+ banana+ leak+ conc_rainfall_water+  tree+ wastewater+ scars+ tilted+ ground_veg+ construction_deposit+ crack+ leaning_wall
          ,data=train.data, cr=TRUE , subn=FALSE , cex.points =0.65)
```



```{r,  fig.width=7, fig.height=10}
sf <- function (y) {
        c('y>=1' = qlogis(mean(y>=1)),
          'y>=2' = qlogis(mean(y>=2)),
           'y>=3' = qlogis(mean(y>=3)),
            'y>=4' = qlogis(mean(y>=4)))
}

s<-with(train.data, summary(as.numeric(risk)~ building+ angle+ EN+ TC+ landfill+ garbage+ banana+ leak+ conc_rainfall_water+  tree+ wastewater+ scars+ tilted+ ground_veg+ construction_deposit+ crack+ leaning_wall
, fun=sf))
s

plot(s, which=1:4, pch=1:4, xlab='logit', main=' ', xlim=c(-5,5), cex.lab=0.7, cex.axis=0.5, cex.sub=0.5)

```


## Predicion on test data Eq 1: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}
predictedLevel1 <- predict(eq_OLR_01, test.data) # predict the levels directly

predictedScores1 <- predict(eq_OLR_01, test.data, type="p") 
 # predict the probabilites

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel1)

p1 <- mean(as.character(test.data$risk) != as.character(predictedLevel1)) #misclassification error
p1 
```

## Predicion on test data Eq 2: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}

predictedLevel2 <- predict(eq_OLR_02, test.data) # predict the levels directly

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel2)

p2 <- mean(as.character(test.data$risk) != as.character(predictedLevel2))
p2
```
## Predicion on test data Eq 3: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}
predictedLevel3 <- predict(eq_OLR_03, test.data) # predict the levels directly

predictedScores1 <- predict(eq_OLR_03, test.data, type="p") 
 # predict the probabilites

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel3)

p3 <- mean(as.character(test.data$risk) != as.character(predictedLevel3))
p3
```
## Predicion on test data Eq 4: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}
predictedLevel4 <- predict(eq_OLR_04, test.data) # predict the levels directly

predictedScores1 <- predict(eq_OLR_04, test.data, type="p") 
 # predict the probabilites

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel4)

p4 <- mean(as.character(test.data$risk) != as.character(predictedLevel4))
p4
```


## Predicion on test data Eq 5: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}
predictedLevel5 <- predict(eq_OLR_05, test.data) # predict the levels directly

predictedScores5 <- predict(eq_OLR_05, test.data, type="p") 
 # predict the probabilites

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel5)

p5 <- mean(as.character(test.data$risk) != as.character(predictedLevel5))
p5
```




## Predicion on test data Eq 6: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}
predictedLevel6 <- predict(eq_OLR_06, test.data) # predict the levels directly

predictedScores6 <- predict(eq_OLR_06, test.data, type="p") 
 # predict the probabilites

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel6)

p6 <- mean(as.character(test.data$risk) != as.character(predictedLevel6))
p6
```




## Predicion on test data Eq 7: http://r-statistics.co/Ordinal-Logistic-Regression-With-R.html

```{r}
predictedLevel7 <- predict(eq_OLR_07, test.data) # predict the levels directly

predictedScores7 <- predict(eq_OLR_07, test.data, type="p") 
 # predict the probabilites

## Confusion matrix and misclassification error
table(test.data$risk, predictedLevel7)

p7 <- mean(as.character(test.data$risk) != as.character(predictedLevel7))
p7
```
```{r}
#Table 

df2 <- data.frame(
  
  "Equations"=c(1:7), 
  "Predicted"=c(1-p1, 
                1-p2,
                1-p3,
                1-p4,
                1-p5,
                1-p6,
                1-p7
              
    
    
  )
  
  
  
)

df2
```

